Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-09-22 manuscript/manuscript.Rmd
Re-roxygenize

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitr")
library("kfigr")
library("knitcitations")
library("parallel")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_reliability)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1, fig.align="center")
options(mc.cores = parallel::detectCores())
```

>>>>

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitr")
library("kfigr")
library("knitcitations")
library("parallel")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_reliability)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1, fig.align="center", warning = FALSE)
options(mc.cores = parallel::detectCores())
```
